Beam-Helicity and Beam-Charge Asymmetries \\ in the Bethe--Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS0607 (v2.1)} \underline{Drafting Committee: DC90 (\today)}

### 2011-12-20 background_and_systematic_dual.tex
Updated paper with the replies to the comments as discussed in the alst drafting meeting. In p[articular, restructured much of chapter 2 into chapter 1.

\section{Background Corrections and Systematic Uncertainties for the
  2006-2007 Data}
The extracted asymmetry amplitudes are subject to systematic uncertainties that
result from a combination of background processes, 
shifts in the missing-mass distributions and various detector and binning
effects determined in the same manner as in refs.~\cite{Air08,Air09}.

@@

The beam polarisation measurement has a total uncertainty of 2.8\% and 3.4\% for the 1996-2005 and 2006-2007 data taking periods respectively,
which is present in the beam-helicity amplitudes and is quoted as an
independent scale uncertainty without consideration in the other presented uncertainties.

The data sample in the exclusive region contains events involving both
production of real photons in which the proton remains intact and
events involving the excitation of the target proton to a $\Delta^+$
resonant state (``associated production''). The recoiling proton is not detected and the calorimeter resolution does not allow separation of the latter events from the rest of the data sample.
No systematic uncertainty is assigned for the contribution from these
events; they are treated as part of the signal. A Monte Carlo
calculation based on the parameterisation from ref.~\cite{Bra76} is
used to estimate the fractional contribution to the event sample from resonant
production in each kinematic bin. The results, called the associated fractions and labelled ``Assoc. fraction'', are shown in the last row of figures~\ref{bsa_xbjrange}--\ref{bca_xbjrange2} in the results section. The method used to perform this estimation is described in detail in
ref.~\cite{Air08}.

>>>>

1\section{Background Corrections and Systematic Uncertainties for the
  2006-2007 Data}
The extracted asymmetry amplitudes are subject to systematic uncertainties that
result from a combination of background processes, 
shifts in the missing-mass distributions and various detector and binning
effects determined in the same manner as in refs.~\cite{Air08,Air09}.

@@

The beam polarisation measurement has total uncertaint\red{ies} of 2.8\% \red{for the 1996-2005 data-taking period} and 3.4\% for the 2006-2007 data taking period. \red{These uncertainties are present} in the beam-helicity amplitudes and \red{are} quoted as independent scale uncertaint\red{ies} without consideration in the other presented uncertainties.

The data sample in the exclusive region contains events involving production of real photons in which the proton remains intact and
events involving the excitation of the target proton to a $\Delta^+$
resonant state (``associated production''). The recoiling proton is not detected and the calorimeter resolution does not allow separation of the latter events from the rest of the data sample.
No systematic uncertainty is assigned for the contribution from these
events; they are treated as part of the signal. A Monte Carlo
calculation based on the parameterisation from ref.~\cite{Bra76} is
used to estimate the fractional contribution to the event sample from resonant
production in each kinematic bin. The results, called the associated fractions and labelled ``Assoc. fraction'', are shown in the last row of figures~\ref{bsa_xbjrange}--\ref{bca_xbjrange2} in the results section. The method used to perform this estimation is described in detail in
ref.~\cite{Air08}.

### 2011-12-20 experiment_and_data.tex
Updated paper with the replies to the comments as discussed in the alst drafting meeting. In p[articular, restructured much of chapter 2 into chapter 1.

An event
was selected as having exactly one photon and one lepton
track detected within the acceptance of the spectrometer.
The event selection is subject to the kinematic constraints 1\,GeV$^{2}$ $<$
Q$^{2}$ $<$ 10\,GeV$^{2}$, 0.03 $<$ $x_{\textrm{B}}$ $<$ 0.35,
$-t < 0.7$\,GeV$^2$, $W^{2}$ $>$
9\,GeV$^{2}$ and $\nu$ $<$ 22\,GeV, where $W$ is the invariant mass of the
$\gamma^{*}p$ system and $\nu$ is the energy of the virtual photon in the target
rest frame. The polar angle between the virtual and real photons was required to
be within the limits 5 mrad $<$
$\theta_{\gamma^{*}\gamma}$ $<$ 45 mrad.

An event sample was selected using a missing-mass technique requiring
that the squared missing-mass $M_{\textrm{X}}^{2}=(q+P-q')^{2}$
of the $e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$ measurement
corresponded to the square of the proton mass within the limits of the
energy resolution of the H{\sc ermes} \red{spectrometer (mainly the calorimeter)}. Here, $q$ is the
four-momentum of the virtual photon, $p$ is the initial four-momentum
of the target proton and $q'$ is the four-momentum of the produced
photon. The ``exclusive region'' was defined as $-$($1.5$\,GeV)$^{2} <
M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in
ref.~\cite{Air09}. This exclusive region was shifted by up to
0.17\,GeV$^{2}$ for certain subsets of the data in order to reflect observed differences in the distributions of the electron and positron data samples~\cite{Bur10}.

@@

The expectation value of the experimental yield $N$ is parameterised as
\begin{equation}
 \langle N(e_{\ell},P_{\ell},\phi)\rangle =
\mathcal{L}(e_{\ell},P_{\ell})\eta(e_{\ell},\phi)\textrm{d}\sigma_{\textrm{UU}}
(\phi)\times
[1+P_{\ell}\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)+e_{\ell}P_{\ell}
\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)+e_{\ell}\mathcal{A}_{\textrm{C}}
(\phi)],
\end{equation}
where $P_\ell$ is the beam polarisation, $\mathcal{L}$ is the integrated luminosity, $\eta$ is the detection
efficiency and d$\sigma_{\textrm{UU}}$ denotes the
cross section for an unpolarised target integrated over both beam charges and
beam helicities. The asymmetries $\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)$,
$\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)$ and
$\mathcal{A}_{\textrm{C}}(\phi)$ are expanded in
$\phi$ as
\begin{equation}
\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi) \simeq \sum^{2}_{n=1}
A_{\textrm{LU,I}}^{\sin(n\phi)}\sin(n\phi) 
+ \sum^{1}_{n=0} A_{\textrm{LU,I}}^{\cos(n\phi)}\cos(n\phi), 
\label{alui_asym}
\end{equation}
\begin{equation}
 \mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi) \simeq 
A_{\textrm{LU,DVCS}}^{\sin\phi}\sin\phi 
+ \sum^{1}_{n=0} A_{\textrm{LU,DVCS}}^{\cos(n\phi)}\cos(n\phi), 
\label{aludvcs_asym}
\end{equation}
\begin{equation}
\mathcal{A}_{\textrm{C}}(\phi) \simeq \sum^{3}_{n=0}
A_{\textrm{C}}^{\cos(n\phi)}\cos(n\phi) 
+ A_{\textrm{C}}^{\sin\phi}\sin\phi,
\label{ac_asym}
\end{equation}
where the approximation is due to the truncation of the infinite
Fourier series that would describe the fitted distribution
  perfectly. Only the $\sin(n\phi)$ terms of the
$\mathcal{A}_{\textrm{LU}}$ asymmetries and the $\cos(n\phi)$ terms of the
$\mathcal{A}_{\textrm{C}}$ asymmetry are \red{motivated by the
  physical processes under investigation}. The other terms
are included as both a consistency check for any off-phase
extraneous harmonics in the data and as a test of the
normalisation of the fit. These terms are expected to be
consistent with zero and are found to be so.

@@

The $A^{\cos(3\phi)}_{\textrm{C}}$ amplitude depends on the
$c_{3,\textrm{unp}}^{\textrm{I}}$ Fourier coefficient and hence the
$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$-function. Although the CFFs
in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$,
where $\alpha_{\textrm{S}}$ is the strong coupling constant.
\begin{table}
\begin{center}
\resizebox{\textwidth}{!} {
\begin{tabular}{|c|c|c|c|c|}
\hline
Asymmetry Amplitude& Fourier Coefficient& Dominant CFF Dependence & Twist-Level & Relative Suppression   \\ 
\hline
\hline
$A_{\textrm{LU,I}}^{\sin\phi}$ & $s_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  2 & --\\
\hline
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ & $s_{2,\textrm{unp}}^{\textrm{I}}$ 
&
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  3 & $1/Q$\\
\hline
\hline
$A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{1, \textrm{unp}}^{\textrm{DVCS}}$ &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3 & $1/Q$ \\
\hline
\hline
$A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2& $\frac{(2-y)^2K}{(1-y)(2-2y+y^2)}$
\\
\hline
$A_{\textrm{C}}^{\cos\phi}$ & $c_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2 & --
\\
\hline
$A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{2,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 & $1/Q$ \\
\hline
$A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{3,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 & $\alpha_{\textrm{S}}/\pi$ \\
\hline
 \end{tabular}
}
\caption{Asymmetry amplitudes that can
be extracted from the available data set, the related Fourier
coefficients, dominant $\mathcal{C}$-function, twist-level and level of
suppression relative to the leading amplitudes at H{\sc ermes} kinematic conditions. {The constant K is defined in ref.~\cite{Bel02b}}.}
\label{tab_amplitudes}
\end{center}
\end{table}

>>>>

An event
was selected as having exactly one photon and one lepton
track detected within the acceptance of the spectrometer.
The event selection is subject to the kinematic constraints 1\,GeV$^{2}$ $<$
Q$^{2}$ $<$ 10\,GeV$^{2}$, 0.03 $<$ $x_{\textrm{B}}$ $<$ 0.35,
$-t < 0.7$\,GeV$^2$, $W^{2}$ $>$
9\,GeV$^{2}$ and $\nu$ $<$ 22\,GeV, where $W$ is the invariant mass of the
$\gamma^{*}p$ system and $\nu$ is the energy of the virtual photon in the target
rest frame. The polar angle between the virtual and real photons was required to
be within the limits 5~mrad $<$
$\theta_{\gamma^{*}\gamma}$ $<$ 45~mrad.

An event sample was selected using a missing-mass technique requiring
that the squared missing-mass $M_{\textrm{X}}^{2}=(q+M_{P}-q')^{2}$
of the $e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$ measurement
corresponded to the square of the proton mass within the limits of the
energy resolution of the H{\sc ermes} \red{spectrometer (mainly the calorimeter)}. Here, $q$ is the
four-momentum of the virtual photon, $M_{P}$ is the initial four-momentum
of the target proton\red{, i.e. the mass of the proton,} and $q'$ is the four-momentum of the produced
photon. The ``exclusive region'' was defined as $-$($1.5$\,GeV)$^{2} <
M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in
ref.~\cite{Air09}. This exclusive region was shifted by up to
0.17\,GeV$^{2}$ for certain subsets of the data in order to reflect observed differences in the distributions of the electron and positron data samples~\cite{Bur10}.

@@

The expectation value of the experimental yield $N$ is parameterised as
\begin{equation}
 \langle N(e_{\ell},P_{\ell},\phi)\rangle =
\mathcal{L}(e_{\ell},P_{\ell})\eta(e_{\ell},\phi)\textrm{d}\sigma_{\textrm{UU}}
(\phi)\times
[1+P_{\ell}\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)+e_{\ell}P_{\ell}
\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)+e_{\ell}\mathcal{A}_{\textrm{C}}
(\phi)],
\end{equation}
where $P_\ell$ is the beam polarisation, $\mathcal{L}$ is the integrated luminosity, $\eta$ is the detection
efficiency and d$\sigma_{\textrm{UU}}$ denotes the
cross section for an unpolarised target integrated over both beam charges and
beam helicities. The asymmetries $\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)$,
$\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)$ and
$\mathcal{A}_{\textrm{C}}(\phi)$ are expanded in
$\phi$ as
\begin{equation}
\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi) \simeq \sum^{2}_{n=1}
A_{\textrm{LU,I}}^{\sin(n\phi)}\sin(n\phi) 
+ \sum^{1}_{n=0} A_{\textrm{LU,I}}^{\cos(n\phi)}\cos(n\phi), 
\label{alui_asym}
\end{equation}
\begin{equation}
 \mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi) \simeq 
A_{\textrm{LU,DVCS}}^{\sin\phi}\sin\phi 
+ \sum^{1}_{n=0} A_{\textrm{LU,DVCS}}^{\cos(n\phi)}\cos(n\phi), 
\label{aludvcs_asym}
\end{equation}
\begin{equation}
\mathcal{A}_{\textrm{C}}(\phi) \simeq \sum^{3}_{n=0}
A_{\textrm{C}}^{\cos(n\phi)}\cos(n\phi) 
+ A_{\textrm{C}}^{\sin\phi}\sin\phi,
\label{ac_asym}
\end{equation}
where the approximation is due to the truncation of the infinite
Fourier series that would describe the fitted distribution
  perfectly. Only the $\sin(n\phi)$ terms of the
$\mathcal{A}_{\textrm{LU}}$ asymmetries and the $\cos(n\phi)$ terms of the
$\mathcal{A}_{\textrm{C}}$ asymmetry are \red{motivated by the
  physical processes under investigation}. The other terms
are included both \red{as} a consistency check for any off-phase
extraneous harmonics in the data and as a test of the
normalisation of the fit. These terms are expected to be
consistent with zero and are found to be so.

@@

The $A^{\cos(3\phi)}_{\textrm{C}}$ amplitude depends on the
$c_{3,\textrm{unp}}^{\textrm{I}}$ Fourier coefficient and hence the
$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$-function. Although the CFFs
in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$,
where $\alpha_{\textrm{S}}$ is the strong coupling constant. Table~\ref{tab_amplitudes} presents the asymmetry amplitudes extracted in this analysis and the
related Fourier coefficients, dominant $\mathcal{C}$-function, twist-level and level of suppression.
\begin{table}
\begin{center}
\resizebox{\textwidth}{!} {
\begin{tabular}{|c|c|c|c|c|}
\hline
Asymmetry Amplitude& Fourier Coefficient& Dominant CFF Dependence & Twist-Level & Relative Suppression   \\ 
\hline
\hline
$A_{\textrm{LU,I}}^{\sin\phi}$ & $s_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  2 & --\\
\hline
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ & $s_{2,\textrm{unp}}^{\textrm{I}}$ 
&
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  3 & $1/Q$\\
\hline
\hline
$A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{1, \textrm{unp}}^{\textrm{DVCS}}$ &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3 & $1/Q$ \\
\hline
\hline
$A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2& $\frac{(2-y)^2K}{(1-y)(2-2y+y^2)}$
\\
\hline
$A_{\textrm{C}}^{\cos\phi}$ & $c_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2 & --
\\
\hline
$A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{2,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 & $1/Q$ \\
\hline
$A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{3,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 & $\alpha_{\textrm{S}}/\pi$ \\
\hline
 \end{tabular}
}
\caption{Asymmetry amplitudes that can
be extracted from the available data set, the related Fourier
coefficients, dominant $\mathcal{C}$-function, twist-level and level of
suppression relative to the leading amplitudes at H{\sc ermes} kinematic conditions. {The constant K is defined in ref.~\cite{Bel02b}}.}
\label{tab_amplitudes}
\end{center}
\end{table}

### 2011-12-20 frame_dual.tex
Updated paper with the replies to the comments as discussed in the alst drafting meeting. In p[articular, restructured much of chapter 2 into chapter 1.

\begin{document}
\title{Beam-Helicity and Beam-Charge Asymmetries \\
        in the Bethe--Heitler and DVCS processes on \\
        an Unpolarised Proton Target
  	\underline{Paper Tag: PDVCS0607 (v2.0)}
        \underline{Drafting Committee: DC90 (\today)}
}

@@

\abstract{
Beam-helicity and beam-charge asymmetries in the hard exclusive leptoproduction of real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
are extracted from the H{\sc ermes} data set of 2006-2007 using a
missing-mass event selection technique. The beam-charge asymmetry
amplitudes extracted from the new data set are more
precise than those extracted from the earlier data
set of 1996-2005 previously analysed in the same manner by \red{\sc{Hermes}}. Results from the two data sets are found to be
compatible with each other. Combined results from these data sets are
extracted and represent the most \red{precise asymmetry amplitude measurements made in the H{\sc ermes} kinematic region using a missing-mass event selection technique.}
}
\keywords{lepton-nucleon scattering}

>>>>

\begin{document}
\title{Beam-Helicity and Beam-Charge Asymmetries \\
        in the Bethe--Heitler and DVCS processes on \\
        an Unpolarised Proton Target
  	\underline{Paper Tag: PDVCS0607 (v2.1)}
        \underline{Drafting Committee: DC90 (\today)}
}

@@

\abstract{
Beam-helicity and beam-charge asymmetries in the hard exclusive leptoproduction of real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
are extracted from the H{\sc ermes} data set of 2006-2007 using a
missing-mass event selection technique. The asymmetry
amplitudes extracted from the new data set are more
precise than those extracted from the earlier data
set of 1996-2005 previously analysed in the same manner by \red{\sc{Hermes}}. Results from the two data sets are found to be
compatible with each other. Combined results from these data sets are
extracted and represent the most \red{precise asymmetry amplitude measurements made in the H{\sc ermes} kinematic region using a missing-mass event selection technique.}
}
\keywords{lepton-nucleon scattering}

### 2011-12-20 results_dual.tex
Updated paper with the replies to the comments as discussed in the alst drafting meeting. In p[articular, restructured much of chapter 2 into chapter 1.

\section{Results}
Results for the beam-helicity and beam-charge asymmetry amplitudes extracted separately from previously published 1996-2005 and the new 2006-2007 hydrogen data sets are presented in figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}. Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$. All of the extracted asymmetry amplitudes are subject to a fractional contribution to the event yield from associated production (``Assoc. fraction''), which is shown in the bottom row of each figure. The beam-helicity asymmetry amplitudes are subject to an additional scale uncertainty from the measurement of the beam polarisation, which is stated in the captions of the figures.
\begin{figure}
\begin{center}
\includegraphics[width=15cm,keepaspectratio]{bsadvcsplots_eml_par13_bin6_pic_0607_9605_cluster_dual}
  \caption{Beam-helicity asymmetry amplitudes extracted separately from
the 1996-2005 (open triangles) and 2006-2007 (filled squares)
hydrogen data. The inner error bars represent the statistical uncertainties, while total error bars denote the statistical and systematic uncertainties added in quadrature.  
An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
2006-2007 data respectively is present in the amplitudes due to the imprecision of
the beam polarisation measurement. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bsa_0607}
\end{center}
 \end{figure}

A statistical test was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from the two data sets. Only the statistical uncertainties were employed in this test as the largest contributions to the systematic uncertainties are largely correlated. This test revealed no significant evidence for incompatibility between the data sets. The beam-helicity and beam-charge asymmetry amplitudes can therefore be extracted from the complete hydrogen data set recorded during the entire experimental operation of H{\sc ermes}.
\begin{figure}
\begin{center}
 \includegraphics[width=15cm,keepaspectratio]{bcaplots_eml_par13_bin6_pic_cluster_0607_9605_withassoc_dual}
  \caption{Beam-charge asymmetry amplitudes extracted separately from the 1996-2005 (open triangles) and 2006-2007 (filled squares) hydrogen data.
The inner error bars represent the statistical uncertainties, while the total error bars denote the statistical and systematic uncertainties added in quadrature. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bca_0607}
\end{center}
 \end{figure}

\begin{figure}
 \begin{center}
 \includegraphics[width=15cm]{bsadvcsplots_eml_par13_bin6_release_all_pic_cluster_dual_update_1.pdf}
  \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
from 1996 until 2007. The error bars (bands) represent the statistical
(systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the imprecision of
the beam polarisation measurement. Solid and dashed lines show model calculations from~\cite{Kum09}; calculations from Ref.~\cite{Liu11} are shown as dashed-dotted lines. See text for details. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
  \label{bsa_xbjrange}
 \end{center}
\end{figure}

@@

\begin{figure}
 \begin{center}
 \includegraphics[width=15cm]{bsadvcsplots_tc_xbjrange_eml_par13_bin6_9607_pic_dual}
  \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges. The error bars (bands) represent the statistical (systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the imprecision of the beam polarisation measurement.}
  \label{bsa_xbjrange2}
 \end{center}
\end{figure}

>>>>

\section{Results}
Results for the beam-helicity and beam-charge asymmetry amplitudes extracted 
\red{in Ref.~\cite{fd} from the previously published 1996-2005 data set} and \red{the results extracted from the 2006-2007 hydrogen data sets in this work} are \red{compared} in figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}. Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$. All of the extracted asymmetry amplitudes are subject to a fractional contribution to the event yield from associated production (``Assoc. fraction''), which is shown in the bottom row of each figure. The beam-helicity asymmetry amplitudes are subject to an additional scale uncertainty from the measurement of the beam polarisation, which is stated in the captions of the figures.
\begin{figure}
\begin{center}
\includegraphics[width=15cm,keepaspectratio]{bsadvcsplots_eml_par13_bin6_pic_0607_9605_cluster_dual}
  \caption{Beam-helicity asymmetry amplitudes extracted separately from
the 1996-2005 (open triangles) and 2006-2007 (filled squares)
hydrogen data. The inner error bars represent the statistical uncertainties, while total error bars denote the statistical and systematic uncertainties added in quadrature.  
An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
2006-2007 data respectively is present in the amplitudes due to the \red{uncertainty} of
the beam polarisation measurement. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bsa_0607}
\end{center}
 \end{figure}

A statistical test \red{(Student's test)} was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from the two data sets. Only the statistical uncertainties were employed in this test as the largest contributions to the systematic uncertainties are largely correlated\red{, i.e. effects from detector resolution, acceptance and smearing}. This test revealed no significant evidence for incompatibility between the data sets. The beam-helicity and beam-charge asymmetry amplitudes can therefore be extracted from the \red{entire} hydrogen data set recorded during the entire experimental operation of H{\sc ermes}.
\begin{figure}
\begin{center}
 \includegraphics[width=15cm,keepaspectratio]{bcaplots_eml_par13_bin6_pic_cluster_0607_9605_withassoc_dual}
  \caption{Beam-charge asymmetry amplitudes extracted separately from the 1996-2005 (open triangles) and 2006-2007 (filled squares) hydrogen data.
The inner error bars represent the statistical uncertainties, while the total error bars denote the statistical and systematic uncertainties added in quadrature. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bca_0607}
\end{center}
 \end{figure}

\begin{figure}
 \begin{center}
 \includegraphics[width=15cm]{bsadvcsplots_eml_par13_bin6_release_all_pic_cluster_dual_update_1.pdf}
  \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
from 1996 until 2007. The error bars (bands) represent the statistical
(systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the \red{uncertainty} of
the beam polarisation measurement. Solid and dashed lines show model calculations from~\cite{Kum09}; calculations from Ref.~\cite{Liu11} are shown as dashed-dotted lines. See text for details. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
  \label{bsa_xbjrange}
 \end{center}
\end{figure}

@@

\begin{figure}
 \begin{center}
 \includegraphics[width=15cm]{bsadvcsplots_tc_xbjrange_eml_par13_bin6_9607_pic_dual}
  \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges. The error bars (bands) represent the statistical (systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the \red{uncertainty} of the beam polarisation measurement.}
  \label{bsa_xbjrange2}
 \end{center}
\end{figure}
